Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
future work

\section{\uppercase{Future work}}
\label{sec:future}

>>>>

\section{\uppercase{Future work}}
\label{sec:future}
The first task that we should have keep in mind after this study is to upgrade the interconnection network to one more focused on HPC.
So that, porting the setup and the tests to an infrastructure with an Infiniband network would shed light on the viability of this kind of solutions for HPC.

Looking for real situations where the performance is not so important as the flexibility to provide more accelerators, 
would drive us to take the first steps through tools for easily deploying programming computer labs with the necessity for GPU.

Finally, to bring in more strategies to decide where a remote GPUs was created and assigned to a physical device, would be an interesting task to carry out. 
With more scheduling policies the flexibility given by the GPGPU module for Openstack should increase.
